Viscous Transport in Eroding Porous Media

### 2019-07-31 docs/transport/erosion_transport.tex
add new figs in transport paper
working on 20 body example

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 nearly touching bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider 20 eroding bodies initially placed in $[-1,1] \times
[-1,1]$.  The background flow is the Hagen-Poiseuille flow
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right],
\end{align}
where the flow rate $U$ is chosen so that the pressure drop from $x=-2$
to $x=2$ is held fixed at 2.  For equispaced instances of the
configuration are plotted in Figure~\ref{fig:Eroding20vort}.  The color
in these plots is the vorticity, and this can be used to determine
regions of high and low erosion---erosion happens fastest along regions
of the eroding bodies with a large vorticity in magnitude.  In
Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
function of normalized time.  Initially, 62\%  of the geometry eroded
bodies corresponding to a porosity of $0.38$.  As the bodies erode, the
area fraction decreases towards 0.  The trend of the area fraction
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(a)),
but with a larger initial area fraction.  We also compute the flow rate
$U$ required to maintain a constant pressure drop across the channel in
Figure~\ref{fig:Eroding20flowrate}(b).  Again, the trend of $U$
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(b)),
except that the initial flow rate is an order of magnitude smaller
because of the larger initial area fraction.

@@

{\color{red}
We
measure the area occupied by bodies 
during the eroding and record the flow rate $U$ quantifily in log scale
during the eroding in Fig.~\ref{fig:Eroding20flowrate}. 
Since we simulate the erosion by applying fixed pressure drop 
the flow rate $U$ is small when there are many bodies in the fluid and 
when the area fraction is getting smaller $U$ is getting larger.
In Fig.~\ref{fig:Eroding20flowrate}, 62.32\% of area of $[-1,1] \times
[-1,1]$ is occupied by 20 bodies initially and the flow rate $U$ starts from $9.86\times 10^{-5}$. 
Then the eroding speed is increasing
when more and more bodies are vanished in the fluid and 
the maximum eroding speed happens when the area fraction equals 7.57\% 
which is occupied by 8 bodies.
When all the bodies have vanished completely the flow rate $U$ is equal to 1.
In Fig.~\ref{fig:Eroding20flowrate}(b), the flow rate $U$ increases exponentially 
with growth rate close to $\ln10^4$. }

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/porosity20dense}
\todo[inline]{SH: Make the y-limits of this figure go from 0 to 0.7 ...
no need to make it go below 0}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20flowrate}(a) The area fraction of 20 nearly
 touching eroding bodies and the eroding speed versus time. 
(b) The incoming flow rate of $U$ in log scale versus time. 
Under fixed pressure drop condition, $U$ will be small initially,
increase when bodies are eroding, and grow exponentially 
to 1 when there is no body in the fluid. }
\end{figure}

Snapshots of the
bodies at four equispaced times are shown in
Figure~\ref{fig:Eroding20vort}.   The colormap is the vorticity which is
equivalent to the shear stress when restricted to the eroding bodies.
Therefore, erosion is fastest in regions where the magnitude of the
vorticity is largest.

Initially, several of the eroding bodies are close to the outer wall.
In particular, with $h=L_2/N_\out$, the distance between bodies 1, 6,
13, and 15 are $1.3h$, $2.9h$, $2.8h$, and $1.3h$, respectively.  In
addition, since each body is discretized with $N_\iin=256$ points, the
distance between several pairs of eroding bodies is too small to be
accurately resolved at the prescribed resolution.  Particular pairs
include bodies 1 \& 6, 3 \& 9, 6 \& 8, and 14 \& 18.  By using the
Barycentric quadrature rule, the interaction between these
nearly-touching bodies can be accurately resolved at the prescribed
resolution.

In~\cite{qua-moo2018}, we observed that erosion causes the space
between nearly touching bodies to quickly expand, and flat faces develop
along the region of near contact.  This qualitative behavior is also
observed in Figure~\ref{fig:Eroding20vort}, such as between bodies 3
\&4 and 15 \& 16.  However, by resolving bodies that are
much closer to one another when compared to our previous
work~\cite{qua-moo2018}, we see that it is possible for very little
erosion to occur between a pair of bodies.  In particular, for pairs of
bodies where the channel between the bodies is nearly perpendicular to
the main flow direction (bodies 1 \& 6, 3 \& 9, and 5 \& 13), there is
very little shear stress and the effect of erosion is slight.

In this example, we also observe that erosion creates a network of
channels from the inlet to outlet where the velocity and vorticity, and
therefore erosion rate, are much larger than the other regions.  These
channels can be further visualized by considering the streamlines at
several configurations of the eroding body.  In
Figure~\ref{fig:Eroding20tracer}, we simulate 200 tracers that are
initially to the left of the porous region and equispaced in $y$.  There
are two clear region where the tracers pass through the geometry
much faster than the other regions.  To illustrate the ability of the
Barycentric quadrature formula, streamlines very close to the eroding
bodies are illustrated in the last frame of Figure~\ref{fig:Eroding20tracer}.

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b30}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b90}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b150}\\

\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b210}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270_zoom}\\

%\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b210}
%\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b240}
%\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270}
\caption{\label{fig:Eroding20tracer}The trajectories of 200 tracers in
  the fluid with 20 bodies. The five first snapshots are evenly spaced in time.
  The tracers are evenly spread in the $y$-direction and released at
  $x=-1$. The bottom right frame is a zoom window of the bottom middle frames. 
Since we use a Barycentric quadrature rule
  and the fourth order Runge Kutta method, the tracers can be very close
  to but not penetrate the bodies.}
\end{center}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Cauchy Integral Representation of the Pressure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%The pressure of the double-layer potential is
%\begin{align}
%  p(\xx) = -\frac{1}{\pi} \int_{\bd\Omega} \frac{1}{\rho^2}
%    \left(1 - 2 \frac{\rr \otimes \rr}{\rho^2} \right) \nn
%    \cdot \eeta(\yy) \, ds_\yy.
%\end{align}
%
%
%

>>>>

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_vort}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_vort}
\includegraphics[width = 0.33 \textwidth]{./figs/1b_0d4r0d1h_vort}
\caption{\label{fig:NearWall_vort} }
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 nearly touching bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider 20 eroding bodies initially placed in $[-1,1] \times
[-1,1]$.  The background flow is the Hagen-Poiseuille flow
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right],
\end{align}
where the flow rate $U$ is chosen so that the pressure drop from $x=-2$
to $x=2$ is held fixed at 2.  We start by analyzing the effect of
erosion on the area fraction and the flow rate.  In
Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
function of normalized time.  Initially, 62\%  of the geometry eroded
bodies corresponding to a porosity of $0.38$.  As the bodies erode, the
area fraction decreases towards 0.  The trend of the area fraction
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(a)),
but with a larger initial area fraction.  We also compute the flow rate
$U$ required to maintain a constant pressure drop across the channel in
Figure~\ref{fig:Eroding20flowrate}(b).  Again, the trend of $U$
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(b)),
except that the initial flow rate is an order of magnitude smaller
because of the larger initial area fraction.  Starting around normalized
time $0.2$, Figure~\ref{fig:Eroding20flowrate}(b) is roughly linear
which indicates that the flow rate can be written as a power law.  Using
a line of best fit, the flow rate is approximately \begin{align} U
\approx \left(\frac{t}{t_f}\right)^{15/4}, \end{align}
\todo[inline]{update this with whatever S-H gets} which is the dashed
line in Figure~\ref{fig:Eroding20flowrate}(b).

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/porosity20dense}
\todo[inline]{SH: Make the y-limits of this figure go from 0 to 0.7 ...
no need to make it go below 0}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
\todo[inline]{SH: In this figure, can you superimpose a line of best fit
from about normalized time 0.2 to normalize time 1.  Doing this crudely,
I got a slope of 15/4}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20flowrate}(a) The area fraction of 20 nearly
 touching eroding bodies and the eroding speed versus time. 
(b) The incoming flow rate of $U$ in log scale versus time. 
Under fixed pressure drop condition, $U$ will be small initially,
increase when bodies are eroding, and grow exponentially 
to 1 when there is no body in the fluid. }
\end{figure}

Snapshots of the bodies at four equispaced times are shown in
Figure~\ref{fig:Eroding20vort}.   The colormap is the vorticity which is
equivalent to the shear stress when restricted to the eroding bodies.
Therefore, erosion is fastest in regions where the magnitude of the
vorticity is largest.  Initially, several of the eroding bodies are
close to the outer wall.  In particular, with $h=L_2/N_\out$, the
distance between bodies 1, 6, 13, and 15 are $1.3h$, $2.9h$, $2.8h$, and
$1.3h$, respectively.  In addition, since each body is discretized with
$N_\iin=256$ points, the distance between several pairs of eroding
bodies is too small to be accurately resolved with the trapezoid rule at
the prescribed resolution.  Particular pairs include bodies 1 \& 6, 3 \&
9, 6 \& 8, and 14 \& 18.  By using the Barycentric quadrature rule, the
interaction between these nearly-touching bodies can be accurately
resolved at the prescribed resolution.

@@

In~\cite{qua-moo2018}, we observed that erosion causes the space between
nearly touching bodies to quickly expand, and flat faces develop along
the region of near contact.  This qualitative behavior is also observed
in Figure~\ref{fig:Eroding20vort}, such as between bodies 3 \& 4 and 15
\& 16.  However, by resolving bodies that are much closer to one another
when compared to our previous work~\cite{qua-moo2018}, we see that it is
possible for very little erosion to occur between a pair of bodies.  In
particular, for pairs of bodies where the channel between the bodies is
nearly perpendicular to the main flow direction (bodies 1 \& 6, 3 \& 9,
and 5 \& 13), there is very little shear stress and the effect of
erosion is slight.

In this example, we also observe that erosion creates a network of
channels from the inlet to outlet where the velocity and vorticity, and
therefore erosion rate, are much larger than the other regions.  These
channels can be further visualized by considering the streamlines.  In
Figure~\ref{fig:Eroding20tracer}, we freeze the geometry at the second
time step in Figure~\ref{fig:Eroding20vort}, and we simulate 200
tracers.  The tracers are initially placed at $x=-1$ and equispaced in
$y$.  There are two clear region where the tracers pass through the
geometry much faster than the other regions.  One of these fast regions
is located between the bodies and the solid wall at $y=1$, and the other
cuts through the porous region with the upper part of the channel formed
by bodies 1, 4, 6, and 8.  To illustrate the ability of the Barycentric
quadrature formula, streamlines very close to the eroding bodies are
illustrated in the last frame of Figure~\ref{fig:Eroding20tracer}.

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b30}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b90}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b150}\\
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b210}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270_zoom}
\caption{\label{fig:Eroding20tracer}The trajectories of 200 tracers in
the fluid with 20 bodies. The five first snapshots are evenly spaced in
time.  The tracers are evenly spread in the $y$-direction and released
at $x=-1$. The bottom right frame is a zoom window of the bottom middle
frames.  Since we use a Barycentric quadrature rule and the fourth order
Runge Kutta method, the tracers can be very close to but not penetrate
the bodies.}
\end{center}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Cauchy Integral Representation of the Pressure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%The pressure of the double-layer potential is
%\begin{align}
%  p(\xx) = -\frac{1}{\pi} \int_{\bd\Omega} \frac{1}{\rho^2}
%    \left(1 - 2 \frac{\rr \otimes \rr}{\rho^2} \right) \nn
%    \cdot \eeta(\yy) \, ds_\yy.
%\end{align}
%
%
%
%{\color{red}
%We
%measure the area occupied by bodies 
%during the eroding and record the flow rate $U$ quantifily in log scale
%during the eroding in Fig.~\ref{fig:Eroding20flowrate}. 
%Since we simulate the erosion by applying fixed pressure drop 
%the flow rate $U$ is small when there are many bodies in the fluid and 
%when the area fraction is getting smaller $U$ is getting larger.
%In Fig.~\ref{fig:Eroding20flowrate}, 62.32\% of area of $[-1,1] \times
%[-1,1]$ is occupied by 20 bodies initially and the flow rate $U$ starts from $9.86\times 10^{-5}$. 
%Then the eroding speed is increasing
%when more and more bodies are vanished in the fluid and 
%the maximum eroding speed happens when the area fraction equals 7.57\% 
%which is occupied by 8 bodies.
%When all the bodies have vanished completely the flow rate $U$ is equal to 1.
%In Fig.~\ref{fig:Eroding20flowrate}(b), the flow rate $U$ increases exponentially 
%with growth rate close to $\ln10^4$. }
